Stop Lying to Me: New Visual Tools to Choose the Most Honest Nonlinear Dimension Reduction

### 2025-06-26 paper.qmd

```{r}
#| echo: false
#| fig-cap: "Various plots to help tune the model fit, using the binwidth $a_1$ and low density bin removal. In (a) RMSE against $a_1$, RMSE is going to increase as $a_1$ increases, but just before a big increase is a good choice. Here RMSE steadily increases so there is no clear choice. For comparison in the other displays we have chosen $0.03$ (orange dashed), $0.05$ (blue solid), and $0.08$ (green dotted). Proportion of non-empty bins tends to increase with $a_1$ (b). Removing low count bins changes RMSE substantially (c). The average bin density ($\\bar{d}$) tends to decrease with $a_1$ (d)."
#| label: fig-param-two-curvy
#| out-width: 100%
#| fig-width: 12
#| fig-height: 10
#| fig-pos: H

>>>>

```{r}
#| echo: false
#| fig-cap: "Various plots to help tune the model fit, using the binwidth $a_1$ and low density bin removal. In (a) RMSE against $a_1$, RMSE is going to increase as $a_1$ increases, but just before a big increase is a good choice. Here RMSE steadily increases so there is no clear choice - nevertheless, we have chosen three binwidths, $0.03$ (orange dashed), $0.05$ (blue solid), and $0.08$ (green dotted), to compare in the other plots. Proportion of non-empty bins tends to increase with $a_1$ (b). Removing low count bins changes RMSE substantially (c). The average bin density ($\\bar{d}$) tends to decrease with $a_1$ (d)."
#| label: fig-param-two-curvy
#| out-width: 100%
#| fig-width: 12
#| fig-height: 10
#| fig-pos: H
